\documentclass{article}


\usepackage{ulem}
\usepackage{mathrsfs}

\usepackage{indentfirst}
\setlength{\parindent}{2em}
\usepackage{listings}
\usepackage[usenames,dvipsnames]{xcolor}


\usepackage{graphicx}

\title{The First Week Report}
\author{Lu Guorui}
\date{2018.5.27}
\usepackage[a6paper,left=10mm,right=10mm,top=15mm,bottom=15mm]{geometry}


\begin{document}
\maketitle
\tableofcontents
\newpage

\begin{abstract}
\textit{This is my first week to learn Deep Learning. I mainly learned the courses of the first week,second week and third week in Neural Network and Deep Learning.}
\end{abstract}

\section{Some Frequently Used Concept}
{
\tiny 
\begin{itemize}

\item \textit{Neural Network}
\item \textit{Logistic Regression}

\begin{itemize}

\item \textit{Sigmoid Function:$\sigma(z^{(i)})= \frac{1}{ 1+e^{-z^{(i)}}}$}
\item \textit{Lost (error) Function:$L(\hat{y}^{(i)},y^{(i)})=-(y^{(i)}\log{(\hat{y}^{(i)})}+(1-y^{(i)})\log{(1-\hat{y}^{(i)}})$}
\item \textit{Cost Function:$J(w,b)=\frac{1}{m}\sum\limits_{i=1}^mL(\hat{y}^{(i)},y^{(i)})$}
\end{itemize}

\item \textit{Gradient Decent}
\item \textit{Vectorization}
\item \textit{Broadcasting}
\item \textit{Activation Functions}
\end{itemize}
}

\section{Learning Summary}
    To be honest, it's hard for me follow the teacher. Deep Learning courses requir much knowledge of matrix which is used so flexible in the videos that I was confused most of the time.\par
    Despite all of this, I still gained a lot from this week's study experience. For example, I had a rough idea of what is a neural network which seems to be a arcane and obscure object. And I also learned how to use vectorization to avoid using for-loop in order to improve the program's operating efficiency, which is widely used in Python programming.\par
    Apart from Deep Learning, I also learned how to use Git, Github and Latex, which made so amazed. Git is just like what we usuall call "the regret medicine". It can roll-back at any time I like. And Latex is also a fantastic sortware which can be used to typeset your passage perfectly. When I install the Latex, I had a knowledge of expansion of Ubuntu by using GParted, which took me a whole night to carry out.\par
    The above is all I want to say. There are still a great many things waiting for me to fulfill. I'll keep on studying.


 
\end{document}